Inferring generation-interval distributions from contact tracing data: \\ \emph{in prep, PRSB}

### 2019-03-14 doc/network.tex
trying to make progress

The intrinsic generation-interval distribution provides a direct link between speed (exponential growth rate, $r$) and strength (reproductive number, $\mathcal R$) of an epidemic \citep{wallinga2007generation, park2019practical}.
This link has been widely adopted in outbreak analyses as it allows us to conveniently estimate the reproductive number from quantities that are easier to measure.
However, estimating the \emph{correct} generation-interval distribution is challenging: the observed generation-interval distribution varies depending on how and when it is measured \citep{nishiura2010time, tomba2010some, champredon2015intrinsic, britton2019estimation}.
Here, we decompose variation in the observed generation intervals into spatial and temporal components under a realistic setting where contact tracing data are aggregated over time.
We use simple models to distinguish among different sources of variations in the observed generation intervals.
We provide two methods for correcting temporal bias and test their accuracy under a realistic setting using simulated epidemics.

Generation intervals can be measured either forward, by tracing infectees, or backward, by tracing infectors.

@@

>>>>

The intrinsic generation-interval distribution, which describes the expected time distribution of secondary cases, provides a direct link between speed (exponential growth rate, $r$) and strength (reproductive number, $\mathcal R$) of an epidemic \citep{wallinga2007generation, park2019practical}.
This link has been widely adopted in outbreak analyses as it allows us to conveniently estimate the reproductive number from measurable quantities.
However, determining the \emph{correct} generation-interval distribution is challenging: observed generation-interval distributions can vary depending on how and when it is measured \citep{nishiura2010time, tomba2010some, champredon2015intrinsic, britton2019estimation}.
Here, we decompose variation in the observed generation intervals into spatial and temporal components under a realistic setting where contact tracing data are aggregated over time.
We use simple models to distinguish among different sources of variations in the observed generation intervals.
We provide two methods for correcting temporal bias and test their accuracy using simulations.

Generation intervals can be measured either forward (by tracing the infectees of an infected individual) or backward (by tracing the infector of an infected individual).
Previous studies have characterized changes in these distributions over time by looking at infections that are one generation apart.
Instead, we consider a slightly different scenario in which generation intervals are measured over multiple generations.
This assumption better reflects real intervention strategies because contact tracing is often performed throughout an ongoing epidemic to prevent further infections. 
In this case, the observed generation intervals are derived all infections that occured before the last date on which contact tracing was performed and are subject to right-censoring -- it is not possible to trace infections that did not happen yet.

When the epidemic is growing exponentially, the observed generation-interval distribution will always have a shorter mean than the intrinsic-interval distribution.

@@

\subsection{Deterministic SEIR model}

The Susceptible-Exposed-Infected-Recovered (SEIR)

\subsection{Stochastic SEIR model on a network}

\subsection{Derivation of the individual-based method}
